Performance Optimization of Service Chain for vCPE in Small Networks with OpenFlow Switch

### 2017-03-08 netsoft_paper.tex
fix some small error in flow classication

\subsection{Definition of Ground Truth of Flow in Supervised ML}
Ground truth of a flow can be defined based on server (owner of server, category of service, or name of application providing service in server), client (category or name of application in client, or name of executable file in client), or communication (transport layer protocol). Similar with\cite{Qazi2013} \cite{Iwai2016}, we defined ground truth of a flow based on the application establishing the flow in client for desktop applications and native mobile applications. As for web-based applications, we defined ground truth of a flow based on domain name of web service.

\subsection{Method to Obtain Ground Truth of Flow in Supervised ML}
We install our software on various devices establishing the flows. We call the software Scanner. Scanner has different versions for different operating systems (OSs). For desktop applications on Windows, trainer acts as scanner. It uses Windows API and local port of the flow to obtain the ground truth of the flow. As for Mac OS X, scanner calls the UNIX command “lsof” and parses the result to obtain lists of 5-tuples, process IDs (PIDs), and application names. Then scanner uses the PID and “ps” to obtain corresponding complete application names. As for native mobile applications on iOS, scanner uses a method similar to that used on OS X. However, we have to install package of UNIX command and jailbreak the iPhones before scanner runs.  As for native mobile applications on Android, scanner calls “cat /proc/net/tcp,” “cat /proc/net/tcp6,” and “cat /proc/net/udp,” and parses the results to obtain mappings of 5-tuples and UIDs. Next, the Android API and UIDs are used to obtain corresponding application names as ground truth. Finally, mappings of 5-tuples and application names are obtained. For iOS and Android, scanner has to run in background.

@@

\subsubsection{Accuracy Matrices and Results}
Accuracy Matrices and Results: To evaluate the accuracy, we used precision, recall, and the F-measure (also called the F1 score), as shown in \ref{eqn_1}, \ref{eqn_2}, and \ref{eqn_3} \cite{muc4}. In each round of the tenfold cross validation, we calculated the precision and recall of each category to calculate the F1 score of each category. After ten rounds, we calculated the average F1 scores of each category in ten rounds. Table I presents the F1 scores in each category of the top 40 most popular applications in the testing data set. Next, we calculated the average F1 score of all categories in the ten rounds as 0.9062. The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy even there were up to 137 applications in testing data set. Some applications achieved higher F1 score; we believe this happened because these applications had sufficient training data, simple flow combinations, or rarely query servers that accepted requests from numerous applications. We will gather more data to prove our belief in the future. At least, it achieved high accuracy in overall, enabling QoS to effectively do bandwidth control or distribution at the application level in a local network of enterprise, where number of applications on which network manager wants to do bandwidth control may not be very large. In the future, we will add more applications to our testing data set.

@@

\subsubsection{Performance Analysis}
In each round of 10-fold cross validation, after the flow classification engine received a training data set that had approximately 14659 rules, it spent around 6 minutes building a classification model on a workstation with ordinary hardware, including an Intel® Core™ i5-5200U CPU @ 2.20 GHz with 16 GB of RAM. When we only used supervised ML without our proposed method based on DNS responses, ClassifierLight read the classifying data set and asked the flow classification engine for a classification result. The system had approximately 1418 rules, and required around 5 minutes to verify accuracy. No out of memory errors occurred for the flow classification engine both in building classification models and classifying flows. We think this absence of errors happened because we chose a favorable classification algorithm so that memory usage was frugal and time required to build a model was short, even though the hardware was ordinary; 14659 rules and 99 categories existed in the training data set after name mapping.

>>>>

\subsection{Definition of Ground Truth of Flow in Supervised ML}
Ground truth of a flow can be defined based on server (owner of server, category of service, or name of application providing service in server), client (category or name of application in client, or name of executable file in client), or communication (transport layer protocol, or application layer protocol). Similar with\cite{Qazi2013} \cite{Iwai2016}, we define ground truth of a flow based on the application establishing the flow in client for desktop applications and native mobile applications. As for web-based applications, we define ground truth of a flow based on domain name of web service.

\subsection{Method to Obtain Ground Truth of Flow in Supervised ML}
We install our software on various devices establishing the flows. We call the software scanner. Scanner has different implementation versions for different operating systems (OSs). For desktop applications on Windows, trainer acts as scanner. It uses Windows API and local port of the flow to obtain the ground truth of the flow. As for Mac OS X, scanner calls the UNIX command “lsof” and parses the result to obtain lists of 5-tuples, process IDs (PIDs), and application names. Then scanner uses the PID and “ps” to obtain corresponding complete application names. As for native mobile applications on iOS, scanner uses a method similar to that used on OS X. However, we have to install package of UNIX command and jailbreak the iPhones before scanner runs.  As for native mobile applications on Android, scanner calls “cat /proc/net/tcp,” “cat /proc/net/tcp6,” and “cat /proc/net/udp,” and parses the results to obtain mappings of 5-tuples and UIDs. Next, the Android API and UIDs are used to obtain corresponding application names as ground truth. Finally, mappings of 5-tuples and application names are obtained. For iOS and Android, scanner has to run in background.

@@

\subsubsection{Accuracy Matrices and Results}
Accuracy Matrices and Results: To evaluate the accuracy, we used precision, recall, and the F-measure (also called the F1 score), as shown in \ref{eqn_1}, \ref{eqn_2}, and \ref{eqn_3} \cite{muc4}. In each round of the tenfold cross validation, we calculated the precision and recall of each category to calculate the F1 score of each category. After ten rounds, we calculated the average F1 scores of each category in ten rounds. Table I presents the F1 scores in each category of the top 40 most popular applications in the testing data set. Next, we calculated the average F1 score of all categories in the ten rounds as 0.9062. The results (Table \ref{table:classification_result}) revealed that our system achieved high accuracy even there were up to 137 applications in testing data set, enabling QoS to effectively do bandwidth control or distribution at the application level in an enterprise network. Some applications achieved higher F1 score; we believe this happened because these applications had sufficient training data, simple flow combinations, or rarely query servers that accepted requests from numerous applications. We will gather more data to prove our belief, and add more applications to testing data set in the future.

@@

\subsubsection{Performance Analysis}
In each round of 10-fold cross validation, after the flow classification engine received a training data set that had approximately 13241 rules, it spent around 6 minutes building a classification model on a workstation with ordinary hardware, including an Intel® Core™ i5-5200U CPU @ 2.20 GHz with 16 GB of RAM. When we only used supervised ML without our proposed method based on DNS responses, ClassifierLight read the classifying data set and asked the flow classification engine for a classification result. The system had approximately 1418 rules, and required around 5 minutes to verify accuracy. No out of memory errors occurred for the flow classification engine both in building classification models and classifying flows. We think this absence of errors happened because we chose a favorable classification algorithm so that memory usage was frugal and time required to build a model was short, even though the hardware was ordinary; 13241 rules and 99 categories existed in the training data set after name mapping.
